Brief notes on erosion

### 2017-07-14 docs/TexNotes/Notes.tex
Fixing the folder stucture and adding back files I accidentally deleted

% Basic editing
\newcommand{\tocite}{{\color{blue}(to cite)}}
\newcommand{\vsp}[1]{\vspace{#1 pc} \noindent}
\newcommand{\np}{\newpage \noindent}
% Derivatives
\newcommand{\pd}[2]    { \frac{\partial #1} {\partial #2} }
\newcommand{\ppd}[2]  { \frac{\partial^2 #1}{{\partial #2}^2} }
\newcommand{\pdi}[2] { {\partial_#2} #1 }
\newcommand{\td}[2] { \frac{d #1} { d #2 } }
\newcommand{\grad}{\nabla}
\newcommand {\Lap} {\grad^2}
% Vectors and operators
\newcommand{\bvec}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\left\| #1 \right\|}
\newcommand{\mean}[1]{\left< #1 \right>}
% Specific variables
\newcommand {\bu} {\bvec{u}}
\newcommand{\nhat}{\hat{\bvec{n}}}
\newcommand{\shat}{\hat{\bvec{s}}}
\newcommand{\eps}{\varepsilon}
\newcommand{\atau}{\abs{\tau}}
\newcommand{\thh}{\hat{\theta}}
\newcommand{\GG}{\mathcal{G}}
\newcommand{\Dt}{\Delta t}
\newcommand{\X}{\bvec{X}}
% Domains
\newcommand {\bdry} {\partial B}
\newcommand {\onBdry} {\text{on } \bdry }
\newcommand {\xfar} {\text{as } \abs{\bvec{x}} \to \infty }

@@

@@

>>>>

% Basic editing
\newcommand{\tocite}{{\color{blue}(to cite)}}
\newcommand{\vsp}[1]{\vspace{#1 pc} \noindent}
\newcommand{\np}{\newpage \noindent}
% Derivatives
\newcommand{\pd}[2]    { \frac{\partial #1} {\partial #2} }
\newcommand{\ppd}[2]  { \frac{\partial^2 #1}{{\partial #2}^2} }
\newcommand{\pdi}[2] { {\partial_#2} #1 }
\newcommand{\td}[2] { \frac{d #1} { d #2 } }
\newcommand{\grad}{\nabla}
\newcommand {\Lap} {\grad^2}
% Vectors and operators
\newcommand{\bvec}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\left\| #1 \right\|}
\newcommand{\mean}[1]{\left< #1 \right>}
% Specific variables
\newcommand {\bu} {\bvec{u}}
\newcommand{\nhat}{\hat{\bvec{n}}}
\newcommand{\shat}{\hat{\bvec{s}}}
\newcommand{\eps}{\varepsilon}
\newcommand{\atau}{\abs{\tau}}
\newcommand{\thh}{\hat{\theta}}
\newcommand{\GG}{\mathcal{G}}
\newcommand{\Dt}{\Delta t}
\newcommand{\X}{\bvec{X}}
\newcommand {\bq} {\bvec{q}}
% Domains
\newcommand {\bdry} {\partial B}
\newcommand {\onBdry} {\text{on } \bdry }
\newcommand {\xfar} {\text{as } \abs{\bvec{x}} \to \infty }

@@

\subsection{The vanishing rate of the area}
The rate of area loss is given by
\begin{equation}
\dot{A} = -C \abs{\tau} L
\end{equation}
We then insert the scaling $\abs{\tau} \sim -1/(L \log L)$ and simplify to get
\begin{equation}
\dot{A} = C/\log{A}
\end{equation}
which we solve to get
\begin{equation}
A (1 - \log A) = C (t_f - t)
\end{equation}
In particular, I believe the signs are correct here.

@@

\section{Permeability, conductivity, drag, resistance, and all of that}

Darcy's law is
\begin{equation}
\bq = - \bvec{K} \grad \phi
\end{equation}
where $\bq$ is the specific discharge, $\phi = z + p/\gamma$ is the hydraulic head, and $\gamma = \rho g$. The rank-2 tensor $\bvec{K}$ is the {\em conductivity}, which is related to the {\em permeability} $\bvec{k}$ via $\bvec{K} = \bvec{k} \gamma/\mu$, where $\mu$ is the viscosity of the fluid. The units of conductivity are length-per-time (i.e.~velocity) and the units of permeability are length squared.
Perhaps the most standard parameter to characterize the porous medium is the permeability, so lets focus on that. Let us also eliminate gravity from consideration to get
\begin{equation}
\bq = - \bvec{k} \grad p / \mu
\end{equation}
Consider first an isotropic medium with permeability $k$ (scalar). I propose that we decompose the permeability into the contribution from channel walls and from the embedded bodies $k = k_{c} + k_{b}$. Lets first figure out the contribution from the channel walls $k_c$. Consider flow in a channel of width $2w$ due to a pressure difference of $\Delta p$ occurring over a length $2 \ell$, so that the pressure gradient is $\grad p = -\Delta p/(2 \ell)$. If I did it correctly, the velocity is
\begin{equation}
u(z) = \frac{\Delta p}{4 \mu \ell} (w^2 - z^2)
\end{equation}
Then we can calculate the discharge as
\begin{equation}
q = \frac{1}{2w} \int_{-w}^{w} u(z) dz = \frac{\Delta p w^2}{6 \mu \ell} = - \frac{w^2}{3 \mu} \grad p
\end{equation}
so that the channel permeability is given by
\begin{equation}
k_c = w^2/3
\end{equation}
This result at least has the correct units (length squared).
